---
title: "Introduction to EasyTCGA"
author: "Kliewer"
date: "//2016"
output: html_document
---


Remark that sometimes it is necessary to run the algorithms / particular functions of FirebrowseR 
several times to get the data, i.e. if the output of an algorithm or especially a particular function 
is NULL it does't imply always data absence (the explanation could be a lack of connection to the server)
This error appears especially using the services \code{\link{Analyses.CopyNumber.Genes.All}} and \code{\link{Samples.mRNASeq}}.
Downloading the whole particular data of a cohort often takes much time.


```{r}
source("dn_clinical.R")
cohorts = dn_cohorts()
cohort = "READ"
read.barcodes = dn_patient_barcodes(cohort) 
brca.clinical = dn_clinical_cohort(cohort)
clinical = dn_clinical("ACC", "BLCA", "BRCA")
tcga_participant_barcode = "TCGA-E9-A2JT" # it is a BRCA patient barcode
page.Size = 2000
gene_ID = dn_gene_ID(tcga_participant_barcode, page.Size)
````

```{r}
source("dn_miRNA.R")
cohort = "BLCA"
tcga_participant_barcode = "TCGA-ZF-AA53"  # it is a BLCA patient barcode
page.Size1 = 250
sort_by =  "tcga_participant_barcode"
mir = miRNA_ID[1:10]
obj = dn_miRSeq(mir, cohort, tcga_participant_barcode, sort_by, page.Size1)
page.Size2 = 2000
blca.miRSeq = dn_miRSeq_cohort(cohort, page.Size2) 
```

```{r}
source("dn_mRNA.R")
gene = "AAAS" # "=mRNA_ID[10]"
cohort = "ESCA"
tcga_participant_barcode = c("TCGA-2H-A9GF", "TCGA-LN-A49M") # esca patient barcodes
sort_by = "gene"
page.Size1 = 250
obj = dn_mRNASeq(gene, cohort, tcga_participant_barcode, sort_by, page.Size2)
page_size2 = 2000
esca.mRNASeq = dn_mRNA_cohort(cohort, page.Size)
```

```{r}
source("Reshape.R")
blca.miRSeq_reshaped = reshape.miRSeq(brca.miRSeq)
esca.mRNASeq_reshaped = reshape.mRNASeq(esca.mRNASeq)
```


